%==============================================================
%  HEMAL SHAH - AI / GENAI DEVELOPER RESUME
%  Paste this whole file into a new Overleaf project (main.tex)
%  Compiler: pdfLaTeX  (Overleaf default)
%
%  HONESTY NOTE (delete before exporting):
%  - "Core Skills" = things actually on your CV / built by you.
%  - "Currently Strengthening" = market-demanded skills you do
%    NOT yet have. Keep them ONLY while genuinely learning them.
%    Move a line up to Core Skills once you've shipped something
%    with it. Do not claim them as known in interviews.
%==============================================================
\documentclass[a4paper,8pt]{extarticle}

\usepackage[top=0.4in,bottom=0.35in,left=0.45in,right=0.45in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}

\definecolor{primary}{HTML}{1A1A1A}
\definecolor{accent}{HTML}{2C5F8A}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% --- Section styling -----------------------------------------
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}[\color{accent}\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

\setlist[itemize]{leftmargin=1.2em, itemsep=0pt, topsep=1pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\linespread{0.97}

% --- Helper for experience headings -------------------------
\newcommand{\expitem}[4]{%
  \textbf{#1} \hfill \textbf{#3}\\
  \textit{#2} \hfill \textit{#4}\\
}

\begin{document}

%==============================================================
% HEADER
%==============================================================
\begin{center}
  {\Huge \bfseries \color{primary} Hemal Shah}\\[4pt]
  {\large \color{accent} AI / GenAI Developer}\\[6pt]
  \small
  \href{mailto:22bt04134@gsfcuniversity.ac.in}{22bt04134@gsfcuniversity.ac.in} \quad
  +91-8320278775\\
  Bharuch, Gujarat, India \quad
  \href{https://github.com/hemal9102}{github.com/hemal9102} \quad
  \href{https://hemal9102.github.io/portfolio_HK/}{Portfolio}
\end{center}

%==============================================================
% SUMMARY
%==============================================================
\section{Professional Summary}
Final-year Computer Science engineer specializing in \textbf{AI application development},
\textbf{Retrieval-Augmented Generation (RAG)} systems, and \textbf{backend automation}.
Built and deployed a production GraphRAG platform and multiple LLM-integrated automation
tools across three internships. Strong in Python, FastAPI, and Docker, with hands-on
experience integrating LLM APIs into real-world products.

%==============================================================
% SKILLS
%==============================================================
\section{Technical Skills}
\textbf{AI / GenAI:} Retrieval-Augmented Generation (RAG), GraphRAG, Vector Search,
Embeddings (Sentence-Transformers), LLM API Integration (Groq), Prompt Engineering,
OCR, NLP-based Document Processing\\
\textbf{Backend \& APIs:} Python, FastAPI, REST API Development, JWT Authentication,
Multi-Auth, OAuth 2.0\\
\textbf{Data \& Storage:} PostgreSQL, pgvector, MongoDB, Supabase, Power BI\\
\textbf{DevOps \& Tools:} Docker, Docker Compose, Git, GitHub, CI/CD, Render, Railway,
Linux, n8n (Workflow Automation), FastMCP\\
\textbf{Languages:} Python, JavaScript, C, C++, C\#\\
\textbf{Currently Strengthening:} LangChain, LangGraph, LlamaIndex, Pinecone / ChromaDB,
LLM Fine-tuning, PyTorch
% ^ Keep this line ONLY while genuinely learning these. Move items
%   up to the relevant category once you have shipped a project.

%==============================================================
% EXPERIENCE
%==============================================================
\section{Professional Experience}

\expitem{AI / Automation Developer}{Inddig Media Pvt. Ltd.}{Mar 2026 -- Present}{}
\begin{itemize}
  \item Built and deployed an AI-driven medical appointment system using FastAPI and
        the Google Calendar API, enabling automated scheduling and patient management
        for a healthcare client; completed Google Cloud OAuth verification.
  \item Rebuilt a legacy PHP-based Google Review workflow using n8n automation and
        Claude MCP servers, reducing manual processing for 400+ client profiles.
  \item Developed and launched responsive full-stack websites (HTML/CSS/JS/PHP) for
        local businesses, managing hosting, SSL, and SEO-friendly site structure.
\end{itemize}

\expitem{AI Engineer Intern}{SentimentAI}{Jul 2025}{}
\begin{itemize}
  \item Built an invoice automation system using PDF parsers and OCR to extract
        structured fields (items, prices, totals) from scanned and digital invoices.
  \item Developed a Telegram bot integrated with n8n for conversational document
        Q\&A and file analysis on uploaded PDFs and images.
  \item Created Google Maps and LinkedIn scrapers for lead generation and market
        research, plus an OCR-based PDF text scanner for data-entry automation.
  \item Worked with Python, BeautifulSoup, Puppeteer, the OCR.space API, and n8n
        for scraping, OCR, and API-driven workflow automation.
\end{itemize}

\expitem{AI / Data Science Intern}{Techicom}{Jun 2025 -- Jul 2025}{}
\begin{itemize}
  \item Built a daily sales-prediction model for local vendors to forecast demand and
        optimize inventory; owned the full data pipeline (EDA, preprocessing, feature
        engineering, modeling).
  \item Built an interactive Power BI dashboard visualizing sales trends and demand
        predictions for stakeholders.
\end{itemize}

\expitem{Web Development Intern}{SP Graphics}{Dec 2023 -- Jan 2024}{}
\begin{itemize}
  \item Built a responsive WordPress website (theme customization, Elementor, plugin integration, basic SEO).
\end{itemize}

%==============================================================
% PROJECTS  (strongest first)
%==============================================================
\section{Key Projects}

\textbf{TrendGraphAI} --- Research Intelligence Platform \hfill \textit{Jan 2026 -- Apr 2026}\\
\href{https://github.com/hemal9102/trendgraphAI}{github.com/hemal9102/trendgraphAI}
\textit{\quad Python, FastAPI, GraphRAG, PostgreSQL, pgvector, Groq API, Sentence-Transformers, Docker}
\begin{itemize}
  \item Built a production RAG pipeline: document ingestion $\rightarrow$ chunking
        $\rightarrow$ embedding generation $\rightarrow$ vector retrieval over a
        pgvector store.
  \item Implemented semantic vector search and automated arXiv data extraction for
        research-paper intelligence; containerized with Docker Compose. Major project (team of 4).
\end{itemize}

\textbf{GitLite} --- GitHub-Style Web Application \hfill \textit{Dec 2025}\\
\href{https://hemal9102.github.io/GitLite/}{hemal9102.github.io/GitLite}
\textit{\quad FastAPI, Docker, JWT, Render}
\begin{itemize}
  \item Built a GitHub-style application with FastAPI and JWT authentication;
        containerized with Docker and deployed on Render.
\end{itemize}

\textbf{Telegram AI Bot} --- Conversational Document Assistant\\
\href{https://t.me/Humong_bot}{t.me/Humong\_bot}
\textit{\quad n8n, LLM API, OCR, HTTP Integration}
\begin{itemize}
  \item Built a Telegram bot that extracts text from PDFs/images and returns
        AI-generated responses via an integrated LLM API and automated workflow.
\end{itemize}

\textbf{Chess AI} --- Reinforcement Learning Game \hfill \textit{Apr 2025 -- May 2025}\\
\href{https://github.com/CYPbhai/Chess/}{github.com/CYPbhai/Chess}
\textit{\quad Unity, C\#}
\begin{itemize}
  \item Developed a fully functional chess game in Unity with an AI opponent driven
        by reinforcement learning (team of 4).
\end{itemize}

%==============================================================
% EDUCATION
%==============================================================
\section{Education}
\expitem{B.Tech., Computer Science \& Engineering}{GSFC University, Vadodara --- CGPA: 7.12 / 10}{2022 -- 2026}{}

%==============================================================
% TRAINING
%==============================================================
\section{Training \& Workshops}
\textbf{International Conference ICON-AI-SMT'25} (GSFC University) --- AI in healthcare, cybersecurity \& business intelligence. \quad \textbf{Full-Stack Web Dev Training} (GSFC University) --- AI-assisted development, prompt engineering, API integration.

\end{document}
